---
title: "Alcohol vs Seat choice"
author: "Wayne Jarvis"
date: "Fall 2025"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people sitting in the middle are the highest, (89), the people in the front are second highest, (40), and the number of people sitting in the back are the lowest, (36). However, the standard deviation is different. Lowest to highest it goes back, middle, high.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After observing the P-value which was about 0.000116, I noticed that it's incredibly small. This tells me that there is a significant difference between the values.

```{r}
plot(TukeyHSD(model1))
```

We're looking at the 95% confidence interval. I analyzed the intervals of the Front-Back, Middle-Back, and Middle-Front seats, with 0 indicating the difference between the lines. After careful observation, I noticed that the Front-Back and Middle-Back seats are significantly different. This is because 0 doesn't go through their confidence intervals. Nonetheless, 0 does go through the confidence interval for the Middle-Front seats. This means that there is not a significant differnece between them. 

## Conclusions


